Race results from the twelfth edition of the

### 2021-08-10 inst/volvo.Rmd
tidy up reference
more detail

This short document creates the `volvo` suite of R objects and
presents some preliminary analysis.

@@

Wikipedia contributors, 2019.  \dQuote{2014-2015 Volvo Ocean Race}.
In \emph{Wikipedia, the free encyclopedia}.  Retrieved 22:21, February
28, 2020.
\url{https://en.wikipedia.org/w/index.php?title=2014\%E2\%80\%932015_Volvo_Ocean_Race&oldid=914916131},

>>>>

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

This short document creates the `volvo` suite of R objects and
presents some preliminary analysis.  It refers to the 12th edition of
the Volvo Ocean Race, 2014-2015 in which seven racing teams competed
over nine legs.  Dataset taken from the wikipedia page (see references
below).

@@

Wikipedia contributors, 2019.  "2014-2015 Volvo Ocean Race".
In _Wikipedia, the free encyclopedia_.  Retrieved 22:21, February
28, 2020.
(https://en.wikipedia.org/w/index.php?title=2014\%E2\%80\%932015_Volvo_Ocean_Race&oldid=914916131)
